Generating Images From Captions\\ With Attention

### 2015-10-07 ram_workshop/ram-paper.tex
changes

\subsubsection{Comparison With Other Models}
The quantitative evaluation of generative models has been a subject of ambiguity in a machine learning community. Compared to reporting classification accuracies in discriminative models, the measures defining generative models are intractable most of the times and might not correctly define the real quality of the model. To get a better comparisions between performances of generative models, we report results on two different metrics as well as do some qualitative comparison of different generative models.

@@

As you can see on Figure~\ref{fig:diffmodels}, we generated several samples from prior of each of the current state-of-the-art generative models corresponding to the caption ``A group of people walk on a beach with surf boards". While all of the samples look sharp, the images generated by LAPGAN look more noisy and don't have a very clear structure in them, whereas the images generated by variational models trained with L2 cost function have a watercolor effect on the images.

>>>>

\subsubsection{Comparison With Other Models}
Quantitatively evaluating generative models remains a challenging task in of itself as each method of evaluation suffer from its own specific drawbacks. Compared to reporting classification accuracies in discriminative models, the measures defining generative models are intractable most of the times and might not correctly define the real quality of the model. To get a better comparision between performances of different generative models, we report results on two different metrics as well as do some qualitative comparison of different generative models.

@@

In Figure~\ref{fig:diffmodels}, we generated several samples from the prior of each of the current state-of-the-art generative models, conditioned on the caption ``A group of people walk on a beach with surf boards". While all of the samples look sharp, the images generated by LAPGAN look more noisy and it is harder to make out definite objects don't have a clear structure in them, whereas the images generated by variational models trained with L2 cost function have a watercolor effect on the images.
